### 2018-03-15 paper/3-abstractions.tex
A few more tweaks

% \vspace{-2mm}
% \paragraph{The store.}
A \emph{store}, of type \hs{Store}~\hs{i}~\hs{k}~\hs{v}, associates keys to
values. It is convenient to assume that a store is total, i.e. it contains a
value for every possible key. We therefore also assume that the type of values
is capable of encoding values corresponding to non-existent keys (missing files
or empty cells). The store also holds a value of type \hs{i},
representing the persistent build information maintained by the build
system~--~its ``memory''.
% Given an \hs{i} and a key/value map \store, we can
% \hs{initialise} a store.

@@

\begin{itemize}
    \item The \hs{ideal} store is \emph{consistent} with the \hs{task}, i.e.
    for all possible non-input keys \hs{k}, the result of recomputing the
    \hs{task} matches the value in the \hs{ideal} store:
    \vspace{-1mm}
    \[
    \hs{compute}~\hs{task}~\hs{ideal}~\hs{k}~\hs{==}~\hs{Just}~\hs{(}\hs{getValue}~\hs{ideal}~\hs{k)}.
    \]
    \item The \hs{result} and \hs{ideal} agree on the output \hs{key}, i.e.:
    \vspace{-1mm}
    \[
    \hs{getValue}~\hs{result}~\hs{key}~\hs{==}~\hs{getValue}~\hs{ideal}~\hs{key}.
    \]
    In other words, we require that the output \hs{key} has the correct value,
    but do not impose any restrictions on intermediate keys, therefore
    permitting shallow cloud builds.
    \item The \hs{store}, \hs{result} and \hs{ideal} agree on all input keys
    \hs{k} that belong to the transitive closure of \hs{key}'s dependencies:
    \[
    \,\,\,\,\,\,\,\hs{getValue}~\hs{store}~\hs{k}~\hs{==}~\hs{getValue}~\hs{result}~\hs{k}~\hs{&&}~\hs{getValue}~\hs{store}~\hs{k}~\hs{==}~\hs{getValue}~\hs{ideal}~\hs{k}
    \]
    % where the implementation of \hs{inputs} is provided in the Appendix, which
    % is dedicated to the task dependency analysis.
    This requirement asserts that (i) no inputs were corrupted during the
    build, and (ii)~the \hs{ideal} store has constraints not only on the output,
    but also on the inputs.
\end{itemize}
A build system is \emph{correct} if it produces a correct \hs{result} for any
given \hs{task}, \hs{key} and \hs{store}.
}
\label{def-correct}
\vspace{-2mm}
\rule{\textwidth}{0.4pt}

@@

So much for applicative tasks. What about monadic tasks with dynamic
dependencies? As we have seen in~\S\ref{sec-background-shake}, dynamic
dependencies need to be tracked too. This cannot be done statically; note that
the application of the function \hs{dependencies} to a \hs{Task}~\hs{Monad} will
not typecheck. We need to run a monadic task on a store with concrete values,
which will determine the discovered dependencies. Accordingly, we introduce
the function \hs{track}: a combination of \hs{compute} and \hs{dependencies}
that computes both the resulting value and the list of its dependencies:

@@

\noindent
The implementation uses the standard Haskell \hs{Writer} monad: we instantiate
\hs{f} to \hs{Writer}~\hs{[@@k]}~\hs{v}, and feed
\hs{fetch}~\hs{k}~\hs{=}~\hs{writer}~\hs{(@@getValue}~\hs{store}~\hs{k,}~\hs{[@@k])}
to the task, which in addition to fetching a value from the store, tracks the
corresponding key. Here is an example of \hs{track}ing monadic tasks:

>>>>

% \vspace{-2mm}
% \paragraph{The store.}
A \emph{store}, of type \hs{Store}~\hs{i}~\hs{k}~\hs{v}, associates keys to
values. It is convenient to assume that a store is total, i.e. it contains a
value for every possible key. We therefore also assume that the type of values
is capable of encoding values corresponding to non-existent keys (missing files
or empty cells). The store also holds a value of type \hs{i},
representing the persistent build information maintained by the build
system~--~its ``memory''.
% Given an \hs{i} and a key/value map \store, we can \hs{initialise} a store.

@@

\begin{itemize}
    \item The \hs{ideal} store is \emph{consistent} with the \hs{task}, i.e.
    for all possible non-input keys \hs{k}, the result of recomputing the
    \hs{task} matches the value in the \hs{ideal} store:
    \vspace{-1mm}
    \[
    \hs{compute}~\hs{task}~\hs{ideal}~\hs{k}~\hs{==}~\hs{Just}~\hs{(}\hs{getValue}~\hs{ideal}~\hs{k)}.
    \]
    \item The \hs{result} and \hs{ideal} agree on the output \hs{key}, i.e.:
    \vspace{-1mm}
    \[
    \hs{getValue}~\hs{result}~\hs{key}~\hs{==}~\hs{getValue}~\hs{ideal}~\hs{key}.
    \]
    In other words, we require that the output \hs{key} has the correct value,
    but do not impose any restrictions on intermediate keys, therefore
    permitting shallow cloud builds.
    \item The \hs{store}, \hs{result} and \hs{ideal} agree on all input keys
    \hs{k} that belong to the transitive closure of \hs{key}'s dependencies:
    \[
    \,\,\,\,\,\,\,\hs{getValue}~\hs{store}~\hs{k}~\hs{==}~\hs{getValue}~\hs{result}~\hs{k}~\hs{&&}~\hs{getValue}~\hs{store}~\hs{k}~\hs{==}~\hs{getValue}~\hs{ideal}~\hs{k}
    \]
    This requirement asserts that (i) no inputs were corrupted during the
    build, and (ii)~the \hs{ideal} store has constraints not only on the output,
    but also on the inputs.
\end{itemize}
A build system is \emph{correct} if it produces a correct \hs{result} for any
given \hs{task}, \hs{key} and \hs{store}.
}
\label{def-correct}
\vspace{-2mm}
\rule{\textwidth}{0.4pt}

@@

So much for applicative tasks. What about monadic tasks with dynamic
dependencies? As we have seen in~\S\ref{sec-background-shake}, dynamic
dependencies need to be tracked too. This cannot be done statically; notice that
the application of the function \hs{dependencies} to a \hs{Task}~\hs{Monad} will
not typecheck. We need to run a monadic task on a store with concrete values,
which will determine the discovered dependencies. Accordingly, we introduce
the function \hs{track}: a combination of \hs{compute} and \hs{dependencies}
that computes both the resulting value and the list of its dependencies:

@@

\noindent
The implementation uses the standard Haskell \hs{Writer} monad, which allows us
to record addition information -- a list of keys of type \hs{[@@k]} -- when
computing a task. We instantiate \hs{f} to \hs{Writer}~\hs{[@@k]}~\hs{v}, and feed
\hs{fetch}~\hs{k}~\hs{=}~\hs{writer}~\hs{(@@getValue}~\hs{store}~\hs{k,}~\hs{[@@k])}
to the task, which in addition to fetching a value from the store, tracks the
corresponding key. Here is an example of \hs{track}ing monadic tasks:
